15th International Satisfiability Modulo Theories Competition (SMT-COMP 2020): Rules and Procedures

### 2021-05-01 rules/rules21.tex
updated logics in model validation

\header{Benchmark Selection.}
This track only has the divisions
QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA.
%
This year all but the first are experimental divisions.
%
It will run on a
selection of non-incremental benchmarks with status \texttt{sat} from these
logics (as described on page~\pageref{benchmark-selection}).

>>>>

\header{Benchmark Selection.}
This track has the divisions
QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA,
QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA.
%
This year all UF logics (with uninterpreted functions) are experimental divisions.
%
It will run on a
selection of non-incremental benchmarks with status \texttt{sat} from these
logics (as described on page~\pageref{benchmark-selection}).
